The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
Results intro tables

%Types intro
The results show that certain types of change are more prevalent than others, these results are shown in \ref{table:type_counts}. Analysis of the results showed that enhancive changes were the primary types of change that drive API evolution and that they act as a catalyst for many of the other changes in the API. Updative changes were found to be consequences of enhancive changes, rather than being drivers of evolution. Supporting the users of the API through the combination of preventive and groomative types of change, together formed another strong driver of API evolution. Reductive and adaptive changes, while important, did not strongly drive the evolution of the API. No evidence was found for corrective, performance types of change. Similarly, there was no evidence found for evaluative, consultive nor training activities.

@@

@@

%Lehman Table
% \begin{table}
%        \centering
%        \begin{tabular}[ht]{l|c}
%               \toprule

%               \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
%               Continuing Change                         & True                      \\ \hline
%               Increasing Complexity                     & True                     \\ \hline
%               Self Regulation                           & True                      \\ \hline
%               Conservation of Organisational Stability  & False                     \\ \hline
%               Conservation of Familiarity               & True                      \\ \hline
%               Continuing Growth                         & True                      \\ \hline
%               Declining Quality                         & True                     \\ \hline
%               Feedback System                           & True                      \\

%               \bottomrule

%        \end{tabular}
%        \caption{The applicability of Lehman's laws}
%        \label{table:lehman}
% \end{table}

@@

% \begin{table}
%        \centering
%        \begin{tabular}[ht]{l|c|c}
%               \toprule

%               \textbf{Type}        & \textbf{Main Types}       &\textbf{Secondary Types}   \\ \midrule
%               Enhancive            & 7                         & -                         \\ \hline
%               Corrective           & -                         & -                         \\ \hline
%               Reductive            & 1                         & -                         \\ \hline
%               Adaptive             & 1                         & -                         \\ \hline
%               Performance          & -                         & -                         \\ \hline
%               Preventive           & 2                         & -                         \\ \hline
%               Groomative           & -                         & 5                         \\ \hline
%               Updative             & 1                         & 1                         \\ \hline
%               Reformative          & 1                         & 1                         \\ \hline
%               Evaluative           & -                         & -                         \\ \hline
%               Consultive           & -                         & -                         \\ \hline
%               Training             & -                         & -                         \\

%               \bottomrule

%        \end{tabular}
%        \caption{Identified Types of Change}
%        \label{table:type_counts}
% \end{table}

>>>>

%Types intro
The results show that certain types of change are more prevalent than others, these results are shown in Table \ref{table:type_counts}. Analysis of the results showed that enhancive changes were the primary types of change that drive API evolution and that they act as a catalyst for many of the other changes in the API. Updative changes were found to be consequences of enhancive changes, rather than being drivers of evolution. Supporting the users of the API through the combination of preventive and groomative types of change, together formed another strong driver of API evolution. Reductive and adaptive changes, while important, did not strongly drive the evolution of the API. No evidence was found for corrective, performance types of change. Similarly, there was no evidence found for evaluative, consultive nor training activities.

\begin{table}
       \centering
       \begin{tabular}[ht]{l|c|c}
              \toprule

              \textbf{Type}        & \textbf{Main Types}       &\textbf{Secondary Types}   \\ \midrule
              Enhancive            & 7                         & -                         \\ \hline
              Corrective           & -                         & -                         \\ \hline
              Reductive            & 1                         & -                         \\ \hline
              Adaptive             & 1                         & -                         \\ \hline
              Performance          & -                         & -                         \\ \hline
              Preventive           & 2                         & -                         \\ \hline
              Groomative           & -                         & 5                         \\ \hline
              Updative             & 1                         & 1                         \\ \hline
              Reformative          & 1                         & 1                         \\ \hline
              Evaluative           & -                         & -                         \\ \hline
              Consultive           & -                         & -                         \\ \hline
              Training             & -                         & -                         \\

       \end{tabular}
       \caption{Identified Types of Change}
       \label{table:type_counts}
\end{table}

@@

%Lehman Table
\begin{table}
       \centering
       \begin{tabular}[ht]{l|c}
              \toprule

              \textbf{Law}                              & \textbf{Applicability}    \\ \midrule
              Continuing Change                         & True                      \\ \hline
              Increasing Complexity                     & True                     \\ \hline
              Self Regulation                           & True                      \\ \hline
              Conservation of Organisational Stability  & False                     \\ \hline
              Conservation of Familiarity               & True                      \\ \hline
              Continuing Growth                         & True                      \\ \hline
              Declining Quality                         & True                     \\ \hline
              Feedback System                           & True                      \\

       \end{tabular}
       \caption{The applicability of Lehman's laws}
       \label{table:lehman}
\end{table}

@@

@@
